---
title: "Lab 02 - Plastic waste"
author: "Marq Schieber"
date: "2/13/22"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read.csv("data/plastic-waste.csv")
```

## Exercises

### Exercise 1

```{r plastic-waste-continent}
ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap)) +
  geom_histogram(binwidth = 0.2) +
  facet_wrap(~ continent)

ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap)) +
  geom_density()

ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent, 
                     fill = continent)) +
  geom_density()

```

They all look relatively similar. Asia and North America appear to have the most waste per capita. 

### Exercise 2

```{r plastic-waste-density}

ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent, 
                     fill = continent)) +
  geom_density(alpha = 0.25)
```

### Exercise 3

Is it because color and fill relate directly to variables in the data set, whereas the alpha 

### Exercise 4


```{r plastic-waste-violin}

ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()

```

First time seeing this type of graph. Does a better job showing where countries within each continent cluster. For example, more countries in Africa are low in waste per capita, whereas there are ore countries in North America that are 'higher' in waste per capita than countries that are low.

### Exercise 5

Visualize the relationship between plastic waste per capita and mismanaged plastic waste per capita using a scatterplot. Describe the relationship.

```{r plastic-waste-mismanaged}

ggplot(data = plastic_waste,
           mapping = aes(x = mismanaged_plastic_waste_per_cap,
                         y = plastic_waste_per_cap)) + 
  geom_point()
```

There appears to be a sharp linear trend.

### Exercise 6


```{r plastic-waste-mismanaged-continent}
ggplot(data = plastic_waste,
           mapping = aes(x = mismanaged_plastic_waste_per_cap,
                         y = plastic_waste_per_cap,
                         color = continent,
                         fill = continent)) + 
  geom_point()
```

It appears that for Africa and Europe, as mismanagement increases, plastic waste increases.  

### Exercise 7

Visualize the relationship between plastic waste per capita and total population as well as plastic waste per capita and coastal population. You will need to make two separate plots. Do either of these pairs of variables appear to be more strongly linearly associated?

```{r plastic-waste-population-total}

ggplot(data = plastic_waste,
           mapping = aes(x = plastic_waste_per_cap,
                         y = total_pop)) +
  geom_point()
```

```{r plastic-waste-population-coastal}
ggplot(data = plastic_waste,
           mapping = aes(x = plastic_waste_per_cap,
                         y = coastal_pop)) +
  geom_point()
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
# insert code here
```

## Pro-Tips

### Excercise 3

Try this :D

ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()+
  geom_boxplot(width=.3, fill="green") +
  stat_summary(fun.y=median, geom="point") 
  
### Exercise 5 

Helpful reference:http://www.sthda.com/english/wiki/ggplot2-themes-and-background-colors-the-3-elements



